Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-08-08 paper/ms.tex
edits on the consistency with the ACF

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock.pdf} 
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_f_occ_mock.pdf}
\end{center}  
\caption{Favored regions in parameter space when the constraints on
  the maximal number of consistent mocks is imposed. The results for
  the {\texttt random} methodology (not shown here) are very similar to the ones
  presented here for the {\texttt match} method.
  \label{fig:restriction_mock}}  
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation.pdf} 
\hspace{5mm}  
\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_correlation.pdf} 
\end{center}
\caption{Left: Values for the free parameters ($\theta_{0}$ vs $\beta$) 
in the fitting formula (Eq. \ref{eq:fitting}) for the mean angular
correlation function. Blue dots correspond to simulations and the green cross to
observations by \citet{Hayashino2004}. The error bars in the 
theoretical data correspond to the standard deviation from the
different mocks surveys. Right: Same results as before in the shown in
the $\theta_{0}$-$M_{\rm min}$ plane. This time the observational
constraints are represented by the red rectangle. Blue squares
represent models with $\log_{10} M_{\rm  max}<12.0$, green circles
correspond to models with $\log_{10} M_{\rm max}>12.0$. 
\label{figure:correlation_parameters}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_mass.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_f_occ.pdf}
\end{center}
\caption{Best models parameter space when both the constraints on the
  maximal number of  consistent mocks and the occupation  fraction
  $f_{\rm occ}\leq  0.2$ are included. $M_{\rm min}$ vs $M_{\rm max}$
  (left), $M_{\rm min}$ vs $f_{\rm occ}$ (rigth).
  \label{fig:restriction_mock_and_f_occ_corr}} 
\end{figure*}

Figure \ref{figure:correlation_parameters} shows the main results in a
$\theta_{0}-\beta$  plane where the average and standard deviation
for each mock is shown in comparison with the result derived from
observations.  The error bars in this Figure represents the standard
deviation of the ACF over all the sub-fields in the 15 mock
observations. These error bars are larger than the statistical
uncertainty from the fitting procedure on a single field.

In the left panel Figure \ref{figure:correlation_parameters} we see how
the observational ACF measured by \cite{Hayashino2004} (green dot) is
successful in reducing the total number of possible models. Only those
with angular-correlation length within
$15^{\prime\prime}<\theta_{0}<23^{\prime\prime}$ are considered to
reproduce observations.

In order to better illustrate the results from this test we
show in the right panel of Figure \ref{figure:correlation_parameters} 
the plane $\theta_{0}$-$M_{\rm min}$ for all models. There we divide
the models into two disjoint sets: those with $\log_{10} M_{\rm
    max}<12$ (blue dots) and $\log_{10} M_{\rm
    max}>12$ (green dots). The colored rectangle includes
the parameter region which is consistent with the observational
constraint in $\theta_{0}$. With this restriction we find that most
models with $\log_{10} M_{\rm max}>12$ and  $\log_{10} M_{\rm min}>11.1$ 
can be safely ruled out.

In Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the preferred
models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$
for the {\tt match} method after applying the observational constraints 
in the occupation fraction and the ACF. Here we consider a model
consistent if there is an overlap of $1-\sigma$ in its values for the
correlation length $\theta_0$ and the power $\beta$ in the
correlation function.  As before, we found similar results using the {\tt random} method

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock.pdf} 
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_f_occ_mock.pdf}
\end{center}  
\caption{Favored regions in parameter space when the constraints on
  the maximal number of consistent mocks is imposed. Only the results
  for the {\texttt match} method are shown.
  \label{fig:restriction_mock}}  
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation.pdf} 
\hspace{5mm}  
\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation.pdf} 
%\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_correlation.pdf}  
\end{center}
\caption{Left: Values for the free parameters ($\theta_{0}$ vs $\beta$) 
in the fitting formula (Eq. \ref{eq:fitting}) for the angular
correlation function. Blue dots correspond to simulations and the
green cross to observations by \citet{Hayashino2004} and
\citet{Ouchi2010}. The error bars in the   theoretical data correspond
to the standard deviation from the different mocks surveys. 
%Right:
%Same results in the $\theta_{0}$-$M_{\rm min}$ plane, with the
%observational constraint on $\theta_{0}$ epresented by the red
%rectangle. Blue  squares represent models with $\log_{10} M_{\rm
%  max}<12.0$, green circles correspond to models with $\log_{10}
%M_{\rm max}>12.0$. 
\label{fig:correlation_parameters}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_mass.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_f_occ.pdf}
\end{center}
\caption{Planes $M_{\rm min}$ vs $M_{\rm max}$ (left), $M_{\rm min}$
  vs $f_{\rm occ}$ (rigth). The squares represent the models when both
  th constraints on the maximal number of  consistent mocks and the
  angular correlation function are included. 
  \label{fig:restriction_mock_and_f_occ_corr}} 
\end{figure*}

Figure \ref{fig:correlation_parameters} shows the main results in a
$\theta_{0}-\beta$  plane where the average and standard deviation
over the mocks is shown in comparison with the result derived from
observations.  The error bars in this Figure represents the standard
deviation of the ACF over all the sub-fields in the 15 mock
observations. These error bars are larger than the statistical
uncertainty from the fitting procedure on a single field.

In the left panel Figure \ref{figure:correlation_parameters} we see
how the observational ACF measured by \cite{Hayashino2004} (green dot)
is successful in reducing the total number of possible models. Only
those with angular-correlation length within
$15^{\prime\prime}<\theta_{0}<23^{\prime\prime}$ are considered to
reproduce observations.     {\bf Cual es el resultsdo de Hayashino
  para $\theta_0$?}

In Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the preferred
models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$
for the {\tt match} method. To make this selection we consider a that
a model is consistent with observations if there is a $1-\sigma$
overlap between both the correlation length $\theta_0$ and the power
$\beta$ in the correlation function. Comparing this Figure with the
results shown in Figure \ref{fig:restriction_mock} we see that the
models that were removed were those with highest minimal masses
$M_{\rm min}>10^{11.2}$, for all the values of $M_{\rm max}$, which
had preferentially high occupation fractions of $f_{\rm occ}> 0.5$.

%In order to better illustrate the results from this test we
%show in the right panel of Figure \ref{figure:correlation_parameters} 
%the plane $\theta_{0}$-$M_{\rm min}$ for all models divided in two
%disjoint sets. The first are the models $\log_{10} M_{\rm
%    max}<12$ (blue dots), the second corresponds to $\log_{10} M_{\rm
%    max}>12$ (green dots). The colored rectangle includes
%the parameter region which is consistent with the observational
%constraint in $\theta_{0}$.  With this restriction we find that most

%models with $\log_{10} M_{\rm max}>12$ and  $\log_{10} M_{\rm min}>11.s$ 
%can be safely ruled out.
